### 2014-02-06 docs/reports/finalreport/architecture.tex
revising finalreport and paper

\section{Architecture and Design}
\label{sec:architecture}
The system is designed based on DDD (Data Driven Design) and Multi-Layer Architecture. As it is depicted in Figure \ref{fig:architecture}, the system consists of three main layers : Interface, Business and Data Access Layer. Data is passed between the layers using Model objects.

Interface layer is divided into two main parts. Server- and client-side. Server-side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model. Its main purpose is mapping Model-View objects of Interface Layer to Model objects and passing them to Business Layer and vice versa. Client-side web pages are designed based on MVVM (Model-View, View, Model) model. Tools used for developing the model are explained in Section \ref{sec:tools}.

@@

As well as mentioned architectural design patterns, following implementation design patterns are used:
\begin{itemize}
	\item Dependency Injection and Inversion of Control implemented in Interface Layer
	\item Singleton Repository in Data Access Layer
	\item Unit of Work for handling transactions
\end{itemize}

>>>>

\section{Architecture and Design}
\label{sec:architecture}
The system is designed based on DDD (Data Driven Design) and Multi-Layer Architecture. As depicted in Figure \ref{fig:architecture}, the system consists of three main layers : Interface, Business and Data Access Layer. Data is passed between the layers using Model objects.

The interface layer is divided into two main parts. Server- and client-side. The server-side which is denoted as Application Layer is following the MVVC (Model-View, View, Controller) design model. Its main purpose is mapping Model-View objects of the Interface Layer to Model objects and passing them to the Business Layer and vice versa. Client-side web pages are designed based on the MVVM (Model-View, View, Model) model. Tools used for developing the model are explained in Section \ref{sec:tools}.

@@

As well as the mentioned architectural design patterns, the following implementation design patterns are used:
\begin{itemize}
	\item Dependency Injection and Inversion of Control implemented in Interface Layer
	\item Singleton Repository in Data Access Layer
	\item Unit of Work for handling transactions
\end{itemize}

### 2014-02-06 docs/reports/finalreport/design.tex
revising finalreport and paper

\section{Tools and Technologies}
\label{sec:tools}
In this section, the main applied tools, technologies and libraries are briefly described following by their usage in the system.

\begin{itemize}
	\item \textbf{C\texttt{\#}.NET 4.5:} As the main programming language, the project is being developed on C\texttt{\#}.NET 4.5 using Visual Studio 2013 IDE.
	\item \textbf{ASP.NET 4.5:} It provides the required framework for web programming. MVC.NET is used as the main server side platform.
	\item \textbf{MS SQL Azure:} As the system is deployed on Windows Azure platform, SQL Azure is selected as relational database.
	\item \textbf{Windows Azure:} Some special services like Cache, Storage and Service Bus are widely used in the project.
	\item \textbf{Lucene.NET:} The core of text processing, indexing and search is handled by Lucene. Lucene.NET is implemented by line to line translating from its Java version. While Lucene in Java provides more options, the .NET version is used to keep the integrity of project.
	\item \textbf{LINQToSQL:} Regarding to high integrity of the tool with MS SQL Server, LINQToSQL is used as ORM (Object-Relational Mapping) tool.
	\item \textbf{HunAlign\cite{hunalign}:} A light library which aligns bilingual text on the sentence level. Its input is tokenized and sentence-segmented text in two languages. In the simplest case, its output is a sequence of bilingual sentence pairs (bisentences). In the presence of a dictionary, hunalign uses it, combining this information  with Gale-Church sentence-length information. In the absence of a dictionary, it first falls back to sentence-length information, and then builds an automatic dictionary based on this alignment. Then it realigns the text in a second pass, using the automatic dictionary. The library is used for developing the translation memory in sentence level based on original and translated text.
	\item \textbf{KnockoutJS:} A JQuery-based library for applying MVVM pattern and associating between DOM and data model.
	\item \textbf{BreezeJS:} A handy JQuery-based library for declaring object models on client side and executing HTML Verbs integrated with ASP.NET MVC.
	\item \textbf{AutoMapper:} Widely used for mapping objects specially from Model objects to View-Model ones.
	\item \textbf{AutoFac:} An IoC container integrated for Microsoft .NET which manages the class dependencies.
	\item \textbf{SignalR:} A library for ASP.NET that makes it simple to add real-time web functionality. Using the library, we can easily have server-side code push content to the connected clients as it happens, in real-time. Chat and notification systems are developed using this library.
	\item \textbf{Postsharp:} An framework for developing AOP in .NET.
\end{itemize}

>>>>

\section{Tools and Technologies}
\label{sec:tools}
In this section, the main applied tools, technologies and libraries are briefly described followed by their usage in the system.

\begin{itemize}
	\item \textbf{C\texttt{\#}.NET 4.5:} The main programming language, project is being developed on C\texttt{\#}.NET 4.5 using Visual Studio 2013 IDE.
	\item \textbf{ASP.NET 4.5:} It provides the required framework for web programming. MVC.NET is used as the main server side platform.
	\item \textbf{MS SQL Azure:} As the system is deployed on the Windows Azure platform, SQL Azure is selected as relational database.
	\item \textbf{Windows Azure:} Some special services like Cache, Storage and Service Bus are widely used in the project.
	\item \textbf{Lucene.NET:} The core of text processing, indexing and search is handled by Lucene. Lucene.NET is implemented by line to line translating from its Java version. While Lucene in Java provides more options, the .NET version is used to keep the integrity of project.
	\item \textbf{LINQToSQL:} Regarding to high level of integrity of the tool with MS SQL Server, LINQToSQL is used as ORM (Object-Relational Mapping) tool.
	\item \textbf{HunAlign\cite{hunalign}:} A light library which aligns bilingual text on the sentence level. Its input is tokenized and sentence-segmented text in two languages. In the simplest case, its output is a sequence of bilingual sentence pairs (bisentences). In the presence of a dictionary, hunalign uses it, combining this information  with Gale-Church sentence-length information. In the absence of a dictionary, it first falls back to sentence-length information, and then builds an automatic dictionary based on this alignment. Then it realigns the text in a second pass, using the automatic dictionary. The library is used for developing the translation memory in sentence level based on original and translated text.
	\item \textbf{KnockoutJS:} A JQuery-based library for applying MVVM pattern and associating between DOM and data model.
	\item \textbf{BreezeJS:} A handy JQuery-based library for declaring object models on client side and executing HTML Verbs integrated with ASP.NET MVC.
	\item \textbf{AutoMapper:} Widely used for mapping objects specially from Model objects to View-Model ones.
	\item \textbf{AutoFac:} An IoC container integrated for Microsoft .NET which manages the class dependencies.
	\item \textbf{SignalR:} A library for ASP.NET that makes it simple to add real-time web functionality. Using the library, we can easily have server-side code push content to the connected clients as it happens, in real-time. Chat and notification systems are developed using this library.
	\item \textbf{Postsharp:} An framework for developing AOP in .NET.
\end{itemize}

### 2014-02-06 docs/reports/finalreport/development.tex
revising finalreport and paper

\section{Development}
\label{sec:development}
In this section, some special issues during the development of the platform are described.

\subsection{Order}
Order system is a full client-side web-page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS. By applying MVVM model, the data submitted in each step is stored in View-Model and used in the next steps. The system screen-shots of ordering process are shown in Figure\ref{fig:order-1} and Figure\ref{fig:order-2}.  The payment process is verified by a third-party service which supports different payment cards.

\subsection{Machine Learning's Data Accumulating}
In order to tackle the problem of translators ranking, a system similar to Order is designed. The system aims to accumulate data for Learning To Rank process. Based on query document, it offers three translators and stores client's (evaluator's) choice. In contrast to Order system, it eliminates the pictures and names of translators which prevents bias in final answers by estimators and puts emphasis on the presented criteria. A screen-shot of the system related to selecting the translators is shown in Figure\ref{fig:dataaccumulating}. In the next step, the data gathered by the system is applied on Learning to Rank algorithms which aim to discover the underlying pattern for proposing the best translators. The details are described in seminar lecture related to the project.

\subsection{Text Matching}
Using Lucene, the documents of translators are categorized, indexed and stored based on their languages. In the next step, the similarity between each document and query document is calculated. In order to achieve the final text matching value, the calculated similarities should be aggregated. As the problem is addressed in Seminar lecture, GP2\cite{gp2} algorithm is implemented and used.

\subsection{Translation Memory}
As it is mentioned before, the aim of Translation Memory system is helping the translators to exploit their previous-translated texts in their new translations. In order to develop the system, first HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in the other language. While the algorithm tends to be error-prone in its basic version specially for complex texts, by adding dictionaries and using just rather simple and straightforward texts, reasonable aligned sentences were achieved. At the end, Lucene indexes the text and provides searching abilities.

\subsection{Scheduling}
The system is also designed by following the SPA idea and using pure Java-Script libraries and Web-API. Figure\ref{fig:scheduling} depicts the schedule web-page interface for an arbitrary translator.

\subsection{Chat}
Using Signal-R capabilities, the Chat system is designed and developed. Related interfaces for meeting room as well as chatting with help-desk user are shown in Figure\ref{fig:chat}.

>>>>

\section{Development}
\label{sec:development}
In this section, we describe some special issues during the development of the platform.

\subsection{Order}
The Order system is a full client-side web-page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS. By applying MVVM model, the data submitted in each step is stored in View-Model and used in the next steps. The system screen-shots from the ordering process are shown in Figure \ref{fig:order-1} and Figure \ref{fig:order-2}.  The payment process is verified by a third-party service which supports different payment cards.

\subsection{Machine Learning's Data Accumulating}
In order to tackle the problem of ranking translators, a system similar to Order is designed. The system aims to accumulate data for a Learning To Rank process. Based on the query document, it offers three translators and stores the client's (evaluator's) choice. In contrast to the Order system, it eliminates the pictures and names of translators in order to reduce clients' bias in the final answer and puts emphasis on the presented criteria. A screen-shot of the system related to selecting the translators is shown in Figure \ref{fig:dataaccumulating}. In the next step, the data gathered by the system is applied on Learning to Rank algorithms which aim to discover the underlying pattern for proposing the best translators. The details are described in seminar lecture related to the project.

\subsection{Text Matching}
Using Lucene, the documents of translators are categorized, indexed and stored based on their languages. In the next step, the similarity between each document and query document is calculated. In order to achieve the final text matching value, the calculated similarities should be aggregated. We use GP2\cite{gp2} algorithm to aggregate similarity values.

\subsection{Translation Memory}
As mentioned before, the aim of a Translation Memory system is helping the translators to exploit their previous translated texts in their new translations. In order to develop the system, first the HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in the other language. While the algorithm tends to be error-prone in its basic version specially for complex texts, by adding dictionaries and using just rather simple and straightforward texts, reasonable aligned sentences were achieved. At the end, Lucene indexes the text and provides searching abilities.

\subsection{Scheduling}
The scheduling system is also designed by following the SPA idea and using pure Java-Script libraries and Web-API. Figure \ref{fig:scheduling} depicts the schedule web-page interface for an arbitrary translator.

\subsection{Chat}
Using Signal-R capabilities, we develop the Chat system. Related interfaces for meeting room as well as chatting with help-desk user are shown in Figure \ref{fig:chat}.

### 2014-02-06 docs/reports/finalreport/introduction.tex
revising finalreport and paper

\section{Introduction}
As a hub for professional translation services, the platform offers its customers top-quality translations at reasonable terms. All translations are reviewed and have to provide evidence of the required qualifications stipulated in the standard by means of their résumé.

Using the platform, regardless of geographical location, translators and clients can communicate and proceed the translation. It aims to ease translating text to even not-so-popular languages as well as reduction of final cost.

The developed platform mainly consists of two parts. First, storing profiles of translators developed in registration and  scheduling systems. Additionally, assisting them during translation process by offering a simple translation memory system. Second, providing a platform for clients to search and hire the translators and purchase the orders.

The remain of the report is organized as follows: In Section \ref{sec:scenario}, system requirements and usual scenarios are described in detail. Then in Section \ref{sec:architecture}, system architecture as well as design methods are explained. Applied tools and technologies following with a short description are introduced in Section \ref{sec:tools}. At the end in Section \ref{sec:development}, by demonstrating the final product in some system screen-shots, specific issues in system development are reported.

>>>>

\section{Introduction}
As a hub for professional translation services, the platform offers its customers top-quality translations at reasonable terms. All translators have to provide evidence of the required qualifications by means of their résumé.

Using the platform, regardless of geographical location, translators and clients can communicate and produce the translation. The platform facilitates translating text to even not-so-popular languages.

The developed platform can mainly be divided into two parts. First, translator platform which consists of registration,  scheduling and translation memory system. Second, client platform which facilitates searching and hiring the translators as well as purchasing the orders.

The remainder of the report is organized as follows: In Section \ref{sec:scenario}, system requirements and usual scenarios are described in detail. Then in Section \ref{sec:architecture}, the system architecture as well as design methods are explained. Section \ref{sec:tools} introduces the tools and technologies we applied. Section \ref{sec:development} reports specific issues in the development of the system by demonstrating the final product in a series of system screen-shots.

### 2014-02-06 docs/reports/finalreport/problem.tex
revising finalreport and paper

\section{Scenario and Requirements}
\label{sec:scenario}
In this section, first the usual scenario of the system is described in detail. Then, some specific requirements related to system development are specified.

By registering in the platform, the translators start to declare their profiles. Regarding to each language pair, the price and duration per word is set. In the next step, the translators upload their previous-translated documents. The documents are processed and used in text matching as well as  translation memory systems. As the last step, the translators fill the time table using schedule system. They specify the time slots in which they are ready to work and potentially can be hired by clients.

The client starts searching for translators by uploading a document. Based on four criteria, the system searches and retrieves the three most-related translators. These criteria are cost, delivery time, frequent cooperation and text matching. Related to each criterion, a weight is defined which specifies importance of the criterion from client's point of view.

Using the profiles of the translators as well client's document, the value for each criteria is estimated. Cost is calculated based on price per word and the number of words in the document. Delivery time is estimated using the schedule of translator, duration per word and the number of words in the document. Finally, text matching value is computed by processing the text and aggregating the similarity values between the query document and the previous-translated documents.

After achieving the values of different criteria, the system ranks the translators and represents the three most-related ones to the client. The client chooses one and follows payment process. By purchasing the order, the platform informs the translator and asks for confirmation. During translation, the client and translator are in contact using a chat system. After finishing translation, a qualified proof-reader chosen by client revises the text and may send some corrections to the translator. At the end, the proof-reader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language).

>>>>

\section{Scenario and Requirements}
\label{sec:scenario}
In this section, first the usual scenario of the system is described in detail. Then, the specific requirements related to system development are specified.

By registering in the platform, the translators start to declare their profiles. Regarding to each language pair, the price and duration per word is set. In the next step, the translators upload their previous translated documents. The documents are processed and used in text matching as well as  translation memory systems. As the last step, the translators fill the time table using schedule system. They specify the time slots in which they are ready to work and potentially can be hired by clients.

The client starts searching for translators by uploading a document. Based on four criteria, the system searches and retrieves the three most relevant translators. These criteria are cost, delivery time, frequent cooperation and text matching. Related to each criterion, a weight is defined which specifies the importance of the criterion from the client's point of view.

Using the profiles of the translators as well client's document, the value for each criteria is estimated. Cost is calculated based on price per word and the number of words in the document. Delivery time is estimated using the schedule of the translator, duration per word and the number of words in the document. Finally, a text matching value is computed by processing the text and aggregating the similarity values between the query document and the previous translated documents of all the translators for the desired language pair.

After having calculated the values of different criteria, the system ranks the translators and represents the three most relevant ones to the client. The client chooses one and follows the payment process. By purchasing the order, the platform informs the translator and asks for confirmation. During translation, the client and translator are in contact using a chat system. After finishing the translation, a qualified proof-reader chosen by the client revises the text and may send some corrections to the translator. At the end, the proof-reader assesses the quality of the translation from different points of view (grammar, style, accuracy, content and language) by giving a score (1-5) of each of them.

### 2014-02-06 docs/reports/finalreport/report.tex
rivising report based on Mihai's feedback
revising finalreport and paper

\input{config}
\input{title}

@@

\maketitle
\begin{abstract}
The report explains the details of design and developing process of a translator retrieval platform. The platform can be defined in domain of on-line translation. It aims to suggest an appropriate translator to a client and manages the process of translation till the last step. Besides, by providing a translation memory system translators can exploit their previous translated texts in their new ones. C\texttt{\#}.NET and MS SQL SERVER as main platform and Lucene.NET as text processor are used. The system is designed based on DDD (Data Driven Design) model. Windows Azure is also selected as deployment environment.
\end{abstract}

@@

\bibliographystyle{plain}
\bibliography{report}

>>>>

\newcommand{\figurescaling}{0.7}
\input{config}
\input{title}

@@

\maketitle
\begin{abstract}
The report explains the details of design and developing process of a translator retrieval platform. The platform's objective is to suggest an appropriate translator to a client. It manages the process of translation until the last step. Additionally, by providing a translation memory system translators can exploit their previous translated texts in their new ones. C\texttt{\#}.NET and MS SQL SERVER are used as main platform and Lucene.NET is the text processor. The system is designed based on Data Driven Design (DDD) model. Windows Azure is the deployment environment.
\end{abstract}

@@

\section{Conclusion}
\label{sec:conclusion}
In this report, we explain different aspects of implementing a translator retrieval system. We report designed architecture, applied tool as well as problems and pitfalls during development.

The project bring us deep understanding on development of an expert retrieval system in a web-based platform. During the system implementation, we confront many problems in the area of text processing, searching and information retrieval. Additionally, we try to apply the best practice on system design and develop regarding to software engineering point of view.
\newpage

\listoffigures
\bibliographystyle{plain}
\bibliography{report}

### 2014-02-06 docs/seminar/casestudy.tex
revising finalreport and paper

\section{Case Study}
\label{sec:casestudy}
The data flow of expert searching is depicted in Figure\ref{fig:architecture}. The client submits a document and searches for translators with a specific target language. Based on query document, the framework figures out offered price, delivery time, proficiency of translators and number of cooperation times related to each translator. The result is processing by a ranking system and the most related translators are offered to the client.

As it is shown in Figure\ref{fig:architecture}, the essential components of the framework are \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiler}.

@@

\textit{Ranking} system uses L2R to return the most related translators to the client. The training data is provided by a group of evaluators who are familiar with business of company using an evaluation system. The evaluation suggests three translators and by comparing between their factors, the evaluators choose one. In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture. Applied learning to rank methods and results are described in Section \ref{sec:apply}. \textit{Proficiency Estimator} stores the previous-translated documents in the cloud and indexes them using Lucene library. The similarity between query and indexed documents is used as a base for estimation of translator's proficiency. In order to find a value proficiency, the similarity scores are aggregated. The applied aggregation function is described in Section \ref{sec:apply}. \textit{Scheduler} system figures out the delivery time based on timetable of translators. The scheduler builds a special data structure to outperform the response time. The detail of the process is out of scope of the paper. At last, \textit{Profiler} accumulates personal information, translators' preferences as well as offered price and translation duration per word.

Beside translator, a proofreader selected by the client revises the final translation. As well as reviewing, the proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language). The assessment is defined as a value between one (very bad) to five (perfect). As it is discussed in Section \ref{sec:apply}, it is used to evaluate aggregation algorithms for translator's proficiency.

>>>>

\section{Case Study}
\label{sec:casestudy}
The data flow of expert searching is depicted in Figure\ref{fig:architecture}. The client submits a document and searches for translators with a specific target language. Based on query document, the framework figures out offered price, delivery time, proficiency of translators and number of cooperation times related to each translator. The result is processed by a ranking system and the most related translators are offered to the client.

As it is shown in Figure \ref{fig:architecture}, the essential components of the framework are \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiler}.

@@

\textit{Ranking} system uses L2R to return the most related translators to the client. The training data is provided by a group of evaluators who are familiar with business of company using an evaluation system. The evaluation suggests three translators and by comparing between their factors, the evaluators choose one. In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture. Applied learning to rank methods and results are described in Section \ref{sec:methods}. \textit{Proficiency Estimator} stores the previous-translated documents in the cloud and indexes them using Lucene library. The similarity between query and indexed documents is used as a base for estimation of translator's proficiency. In order to find proficiency value, the similarity scores are aggregated. The applied aggregation function is described in Section \ref{sec:apply}. \textit{Scheduler} system figures out the delivery time based on timetable of translators. The scheduler builds a special data structure to calculate the response time. The detail of the process is out of scope of the paper. At last, \textit{Profiler} accumulates personal information, translators' preferences as well as offered price and translation duration per word.

Beside translator, a proofreader selected by the client revises the final translation. As well as reviewing, the proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language). The assessment is defined as a value between $1$ (very bad) and $5$ (perfect). As it is discussed in Section \ref{sec:apply}, it is used to evaluate aggregation algorithms for translator's proficiency.

### 2014-02-06 docs/seminar/evaluation.tex
revising finalreport and paper

\section{Apply The Methods and Results}
\label{sec:apply}
In this section, we applied different approaches on the platform. By comparing the methods, we aim to discover the most appropriate one regarding to the project's characters and data.

\subsection{Aggregation Functions}
TODO

>>>>

\section{Apply The Methods and Results}
\label{sec:apply}
In this section, we applied different approaches on the platform. By comparing the methods, we aim to discover the most appropriate one regarding to the project's characteristics and data.

\subsection{Aggregation Functions}
In order to compare different aggregation functions, similar to \citet{agg-gp2} three algorithms are selected. $GP2$ as well as $Top1$ and $Top5$ which are two common forms of $TopN$ aggregation algorithm. $TopN$ refers to algorithm that summarizes the $N$ top documents (i.e. $Top1$ only using the top associated document to rank the candidates).

Feedbacks of proof-readers after every translation are used as a basis for evaluating the algorithms. Since feedbacks are a measure for quality of translation, the more similar the ranking of algorithms to feedbacks are the better it is.

The calculation is done based on $181$ records of purchased orders. The coefficient values of applying Pearson Correlation ($r$) and Spearman's Rank Order Correlation ($r_s$) are shown in Table \ref{table:Spearman}. TODO: Significance Test .

The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers. Nevertheless among the introduced algorithms, $GP2$ outperforms the others. In comparison to $Top1$, $Top5$ has slightly better performance. The results are also nearly the same when comparing based on language-pairs.

\begin{table}
\begin{center}
\scalebox{1.2}{
\begin{tabular}{p{1cm}|c|c|c|}
\cline{2-4} & Top1 & Top5 & GP2  \\
\hline \multicolumn{1}{ |c| }{$r$} & 0.018 & 0.063 & 0.117\\
\hline \multicolumn{1}{ |c| }{$r_s$} & 0.052 & 0.087 & 0.145\\
\hline
\end{tabular}
}
\caption{Comparison between algorithms and feedbacks}
\label{table:Spearman}
\end{center}
\end{table}

### 2014-02-06 docs/seminar/introduction.tex
revising finalreport and paper

\section{Introduction}
\label{sec:introduction}
The goal of expertise retrieval is to link humans to expertise areas, and vice versa. In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \cite{er} \cite{er-community-aware}.

With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR and not just traditional document retrieval, such as entity retrieval and expertise retrieval \citep{er-sparse}. The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \cite{trec2005} \cite{er-community-aware}.

Two principal approaches are proposed in \cite{trec2005} based on probabilistic language modeling techniques. They were formalized as so-called candidate models and document models. The candidate-based approach which is also referred to as profile-based method, builds a textual representation of candidate experts and then rank them based on the query. The document models is to first find documents that are relevant to the topic and then locate the experts associated with these documents \cite{er}.

Ranking techniques are mostly one of the essential parts of IR frameworks. In recent years, Learning to Rank (L2R) has been studied extensively specially for document retrieval. It refers to machine learning techniques for training the model in a ranking task \cite{er}. In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \cite{l2r-intro}.

As well as ranking techniques, aggregation functions have a solid effect on the performance of IR systems. Aggregate tasks are those where documents' similarities are not
the final outcome, but instead an intermediary component. In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \citep{agg-learning}.

This paper addresses the problem of searching translators as experts. We have applied Learning to Rank in a candidate-based approach. Besides, different aggregation algorithms related to documents of translators has been studied.

>>>>

\section{Introduction}
\label{sec:introduction}
The goal of expertise retrieval is to link humans to expertise areas, and vice versa. In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \citep{er, er-community-aware}.

With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR and not just traditional document retrieval, such as entity retrieval and expertise retrieval \citep{er-sparse}. The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \citep{trec2005, er-community-aware}.

Two principal approaches are proposed by \citet{trec2005} based on probabilistic language modeling techniques. They were formalized as so-called candidate models and document models. The candidate-based approach, also referred to as profile-based method, builds a textual representation of candidate experts and then ranks them based on the query. The document models first find documents relevant to the topic and then locate the experts associated with these documents \citep{er}.

Ranking techniques are mostly one of the essential parts of IR frameworks. In recent years, Learning to Rank (L2R) has been studied extensively specially for document retrieval. It refers to machine learning techniques for training the model in a ranking task \citep{er}. In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \citep{l2r-intro}.

As well as ranking techniques, aggregation functions have a significant effect on the performance of IR systems. Aggregate tasks are those where documents' similarities are not
the final outcome, but instead an intermediary component. In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \citep{agg-learning}.

This paper addresses the problem of searching translators as experts. We have applied Learning to Rank in a candidate-based approach. Additionally, different aggregation algorithms related to documents of translators have been studied.

### 2014-02-06 docs/seminar/methods.tex
revising finalreport and paper

The effect of different features on aggregation function is studied in \cite{agg-gp2}. As it is shown, number of documents is tightly related such that the performance of different queries are optimal for different values of $N$. Comparing query-based features using statistical measures, it inferred that the features may not, in general, be able to predict the optimal number of documents to aggregate for each query. Individual Expert Features is discussed in the next step. It is shown that relevant experts are associated with a higher ranked document than non-relevant experts. More interestingly, relevant experts are associated with less documents on average.

Macdonald et al.\cite{agg-vote} looks to expert search as a voting problem, where documents vote for the candidates with relevant expertise. Eleven data fusion as well as three statistically different document weighting were tested. In practice, the approach considers both number of documents and expert features regarding to the ranking score of the documents. The results show that while some of adapted voting techniques are most likely outperform others, the proposed approach is effective when using appropriate one.

Later on, focusing on related features discussed before Cummins et al.\cite{agg-gp2} comes up with a novel idea. It uses genetic programming to learn a formula for the weights of document associations within the candidate profiles. The formula denoted as $GP2$ is as follows:

>>>>

The effect of different features on aggregation function is studied in \citet{agg-gp2}. As it is shown, number of documents is tightly related such that the performance of different queries are optimal for different values of $N$. Comparing query-based features using statistical measures, it inferred that the features may not, in general, be able to predict the optimal number of documents to aggregate for each query. Individual Expert Features is discussed in the next step. It is shown that relevant experts are associated with a higher ranked document than non-relevant experts. More interestingly, relevant experts are associated with less documents on average.

\citet{agg-vote} looks to expert search as a voting problem, where documents vote for the candidates with relevant expertise. Eleven data fusion as well as three statistically different document weighting were tested. In practice, the approach considers both number of documents and expert features regarding to the ranking score of the documents. The results show that while some of adapted voting techniques are most likely outperform others, the proposed approach is effective when using appropriate one.

Later on, focusing on related features discussed before \citet{agg-gp2} introduces a new aggregation method. It uses genetic programming to learn a formula for the weights of document associations within the candidate profiles. The formula denoted as $GP2$ is as follows:
